---
title: "EDLD 610 Final Presentation:"
subtitle: "An analysis of internet and social media trends"  
author: "Cameron S. Kay, Stefania R. Ashby, & Ashley L. Miller"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: TRUE
      countIncrementalSlides: TRUE
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)

#load required packages
library(tidyverse)
library(lme4)
library(lmerTest)
library(here)
library(rio)
library(lubridate)
library(cowplot)
library(wesanderson)
library(forcats)
library(pander)
#devtools::install_github("gadenbuie/xaringanthemer")
library(xaringanthemer)
library(magrittr)

#Disable scientific notation
options(scipen = 999)

```

```{r xaringan-themer, include = FALSE}

#This hidden chunk specifies the theme for the slides

mono_accent_inverse(
  base_color = "#3C989E",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono"))

```

# The Dataset

The [Core Trends Survey](http://www.pewinternet.org/dataset/jan-3-10-2018-core-trends-survey/) (2018) from the [Pew Research Center](http://www.pewresearch.org).

--

- *N* = 2,002

--

- Collected between January 3rd and January 10th, 2018

--

- Conducted by telephone (75.02% cell phone; 24.98% landline)

---

# Tidying the Dataset

Step 1: Import the data.

```{r import_data}
df <- import(here::here("data", "dataSPSS.sav"), setclass = "tibble") %>%
  janitor::clean_names() %>%
  characterize()
```

--

```{r look_at_the_data_total, echo = FALSE}
df
```

---

# Tidying the Dataset

.pull-left[
```{r look_at_data_wanted, echo = FALSE}
temp <- import(here::here("data", "dataSPSS.sav"), setclass = "tibble") %>%
  janitor::clean_names()

temp[, c("age", "books1")]

```
]

--

.pull-right[
```{r look_at_data_unwanted, echo = FALSE}
df[, c("age", "books1")]
rm(temp)

df <- import(here::here("data", "dataSPSS.sav"), setclass = "tibble") %>%
  janitor::clean_names()
```
]

---

# Tidying the Dataset

Functional but bulky. 
```{r characterize_allbut_ugly, eval = FALSE}
.rcol <- function(column = NULL, data = df) {
  grep(column, colnames(data))
}

df[, -c(.rcol("age"), 
        .rcol("books1"))] <- characterize(df[, -c(.rcol("age"), 
                                                  .rcol("books1"))])
```

--

Equally functional and far less bulky. 
```{r characterize_allbut_pretty}
df %<>%
  mutate_at(vars(-age, -books1), characterize)
```

---

# Tidying the Dataset

.pull-left[
```{r look_at_age_with_99, echo = FALSE}
df[, c("age")]
```
]

.pull-right[
```{r look_at_age_without_99, echo = FALSE}
df %<>%
  mutate(age = replace(age, age == 99, NA))

df[, c("age")]
```
]

--

```{r look_at_99na_code, eval = FALSE}
df %<>%
  mutate(age = replace(age, age == 99, NA))
```

---

# Tidying the Dataset

Step 2: Remove extraneous rows and columns. 

```{r drop_unneeded_columns}
df %<>%
  select(-comp, 
         -state:-qs1,
         -intmob,
         -home4nw:-device1d,
         -web1f:-web1h, #dropped because we don't have frequency values
         -pial5a:-pial5d,
         -pial11a:-pial11_igbm,
         -marital:-racem4,
         -birth_hisp,
         -partyln:-cellweight)

df %<>%
  filter(eminuse == "Yes") %>%
  select(-eminuse)
```

---

# Tidying the Dataset

Step 3: Tidy!

```{r gather}
df %<>%
  gather(key = "websites", value = "value", starts_with("sns"), starts_with("web"))


```
--
```{r gather_show, echo = FALSE}
df[, c("websites", "value")]
```
---

# Tidying the Dataset

```{r sep}
df %<>%
  separate(websites, into = c("temp", "website"), sep = "[[:digit:]]") 
```
--
```{r sep_show, echo = FALSE}
df[, c("temp", "website", "value")]
```

---

# Tidying the Dataset
```{r spread}
df %<>%
  spread(key = "temp", value = "value")
```

--
```{r spread_show, echo = FALSE}
df[, c("website", "sns", "web")]
```
---

# Tidying the Dataset
```{r combine_cols}
df[which(df[, "web"] == "No, do not do this"), "sns"] <- "Rarely if ever"

df %<>%
  select(-web)
```

--

```{r combine_cols_show, echo = FALSE}
df[, c("website", "sns")]
```
---

# Tidying the Dataset

Step 4: Rename, convert, and recode!

```{r rename}
df %<>%
  rename(id = respid,
         date = int_date,
         int_use_freq = intfreq,
         int_good_society = pial11,
         int_good_self = pial12,
         total_books_read = books1,
         books_print = books2a,
         books_audio = books2b,
         books_elect = books2c,
         race = racecmb,
         income = inc,
         sns_freq_use = sns,
         sns = website)
```

---

# Tidying the Dataset

```{r recode}
df %<>%
  mutate(sns = recode(sns, a = "Twitter",
                           b = "Instagram",
                           c = "Facebook",
                           d = "Snapchat",
                           e = "YouTube"))
```

```{r extra_tidying, echo = FALSE}
#parse date
df %<>%
  mutate(date_date = ymd(date))

#convert factors to factors
df %<>%
  mutate(books_print = factor(books_print),
         books_audio = factor(books_audio),
         books_elect = factor(books_elect),
         sex = factor(sex),
         race = factor(race),
         party = factor(party),
         sns = factor(sns),
         int_good_society = factor(int_good_society),
         int_good_self = factor(int_good_self),
         int_use_freq = factor(int_use_freq),
         sns_freq_use = factor(sns_freq_use))

df %<>%
  mutate(int_good_self    = fct_recode(int_good_self,
                                       "Bad" = "Bad thing",
                                       "Good" = "Good thing",
                                       "Some of both" = "(VOL) Some of both",
                                       "Other" = "(VOL) Don't know",
                                       "Other" = "(VOL) Refused"),
         int_good_society = fct_recode(int_good_society,
                                       "Bad" = "Bad thing",
                                       "Good" = "Good thing",
                                       "Some of both" = "(VOL) Some of both",
                                       "Other" = "(VOL) Don't know",
                                       "Other" = "(VOL) Refused"),
         party            = fct_recode(party,
                                       "Other" = "(VOL) Other party",
                                       "Other" = "(VOL) Don't know",
                                       "Other" = "(VOL) No preference",
                                       "Refused" = "(VOL) Refused"),
         race             = fct_recode(race,
                                       "Asian" = "Asian or Asian-American",
                                       "Black" = "Black or African-American",
                                       "Other" = "Or some other race",
                                       "Mixed" = "Mixed Race"))


df %<>%
  mutate(int_good_society = factor(int_good_society, 
                                   levels = c("Other", 
                                               "Bad", 
                                               "Some of both", 
                                               "Good")),
         int_good_self    = factor(int_good_self, 
                                   levels = c("Other", 
                                              "Bad", 
                                              "Some of both", 
                                              "Good")),
         int_use_freq     = factor(int_use_freq, 
                                   levels = c("(VOL) Don't know", 
                                              "Less often?", 
                                              "Several times a week, OR", 
                                              "About once a day", 
                                              "Several times a day", 
                                              "Almost constantly")),
         sns_freq_use     = factor(sns_freq_use,
                                   levels = c("(VOL) Don't know",
                                              "Rarely if ever",
                                              "Less often",
                                              "Every few weeks",
                                              "A few times a week", 
                                              "About once a day", 
                                              "Several times a day")))

```

---
# Tidying the Dataset

```{r peek_at_cleaning, echo = FALSE}
df[, c("sns", "sns_freq_use")]
```

---
class: inverse, middle, center

# Examining perceptions of social media use

---

# A Bar Chart: Final Product

```{r ash_plot1_prep, echo=FALSE}

plot_data_ash <- df %>% 
  select(age, sex, race, cregion, party, sns, sns_freq_use, int_good_society, int_good_self, int_use_freq)

```

```{r ash_plot1_run, fig.height=8, fig.width=12, fig.align='center', echo=FALSE}
plot_ash1 <- plot_data_ash %>%
  mutate(int_good_self = as.numeric(int_good_self),
         int_good_society = as.numeric(int_good_society)) %>%
  filter(party != "Refused") %>%
  group_by(party) %>%
  summarize(m_age = mean(age),
            m_self = mean(int_good_self),
            m_society = mean(int_good_society)) %>%
  ggplot(aes(x = party, y = m_society)) +
  geom_col(alpha = 0.5, fill = "turquoise3", color = "turquoise4") +
  geom_hline(yintercept = 3.5, color = "red") + #Note that this line represents the overall mean
  theme_bw(base_size = 21) +
  labs(title = "Figure 1.",
       subtitle = "Ratings of how good or bad the internet is for society as a function of political party",
       x = "Political Party", 
       y = "Mean Rating") +
  coord_cartesian(ylim = c(2.5, 4)) 

plot_ash1
```

---

# A Bar Chart's Journey:

First, I put together a dataframe with variables of interest:

```{r ash_plot1_df, eval=FALSE}

plot_data_ash <- df %>% 
  select(age, sex, race, cregion, party, sns, sns_freq_use, 
         int_good_society, int_good_self, int_use_freq)

```

--

Next, I came up with a question:

- Namely, are there differences in **how good people belief the internet is for society** as a function of **political party**?

--

- Do I need to tidy the data any more?

```{r ash_plot1_view}
head(plot_data_ash, 1)
```

---

More data tidying:

```{r ash_plot1_tidy, eval=FALSE}

plot_ash1 <- plot_data_ash %>%
  mutate(int_good_self = as.numeric(int_good_self),
         int_good_society = as.numeric(int_good_society)) %>% #<<
  filter(party != "Refused") %>%
  group_by(party) %>%
  summarize(m_age = mean(age),
            m_self = mean(int_good_self),
            m_society = mean(int_good_society)) #<<

```

--

Plotting the data:

```{r ash_plot1_code, eval=FALSE}

ggplot(plot_ash1, aes(x = party, y = m_society)) +
  geom_col(alpha = 0.5, fill = "turquoise3", color = "turquoise4") +
  geom_hline(yintercept = 3.5, color = "red") + 
  theme_bw() +
  labs(title = "Figure 1.",
       subtitle = "Ratings on a 4 point scale of how good or bad the 
       internet is for society as a function of political party",
       x = "Political Party", 
       y = "Mean Rating") +
  coord_cartesian(ylim = c(2.5, 4))

```

---
class: inverse, middle, center

# Examining social media use frequency

---

# A Line Graph: Final Product

```{r ash_plot2_run, fig.height=8, fig.width=15, fig.align='center', echo = FALSE}

plot_ash2 <- plot_data_ash %>%
  mutate(int_good_self = as.numeric(int_good_self),
         int_good_society = as.numeric(int_good_society),
         int_use_freq = as.numeric(int_use_freq),
         sns_freq_use = as.numeric(sns_freq_use)) %>%
  filter(party != "Refused",
         sns_freq_use != "<NA>",
         sns_freq_use != "(VOL) Don't know")


ggplot(plot_ash2, aes(x = age, y = sns_freq_use)) +
  geom_smooth(aes(group = party, colour = party), method = "lm", se = FALSE) +
  facet_wrap(~sns, nrow = 1) +
  scale_colour_viridis_d() +
  theme_bw(base_size = 21) +
  labs(title = "Figure 2.",
       subtitle = "Relation between age and frequency of social media use as a function of political party and social media site",
       x = "Age", 
       y = "Frequency of social media use",
       colour = "Political party")

```

---

# A Line Graph's Journey

Again, I first came up with a question. This time I wanted to examine how **frequency of social media use** might vary as a function of **age**, **political party**, and **social media site**.

--

```{r ash_plot2_view}
head(plot_data_ash, 1)
```

--

Minor data tidying:

```{r ash_plot2_tidy, eval=FALSE}
plot_ash2 <- plot_data_ash %>%
  mutate(sns_freq_use = as.numeric(sns_freq_use)) %>% #<<
  filter(party != "Refused",
         sns_freq_use != "<NA>",
         sns_freq_use != "(VOL) Don't know") 
```

---

# Plotting the data:

```{r ash_plot2_code, eval=FALSE}
ggplot(plot_ash2, aes(x = age, y = sns_freq_use)) +
  geom_smooth(aes(group = party, colour = party), 
              method = "lm", se = FALSE) +
  facet_wrap(~sns, nrow = 1) +
  scale_colour_viridis_d() +
  theme_bw() +
  labs(title = "Figure 2.",
       subtitle = "The relation between age and frequency of social media use 
       as a function of political party and social media site",
       x = "Age", 
       y = "Frequency of social media use",
       colour = "Political party")
```

---
class: inverse, middle, center

#What happens if we swap out political party for sex?

---

# Another Line Graph: 

```{r ash_plot3_run, fig.height=8, fig.width=15, fig.align='center', echo=FALSE}

ggplot(plot_ash2, aes(x = age, y = sns_freq_use)) +
  geom_smooth(aes(group = sex, colour = sex), method = "lm", se = FALSE, lwd = 2) +
  scale_color_manual(values = c("turquoise3", "purple3")) +
  facet_wrap(~sns, nrow = 1) +
  theme_bw(base_size = 21) +
  labs(title = "Figure 3.",
       subtitle = "The relation between age and frequency of social media use as a function of sex and social media site",
       x = "Age", 
       y = "Frequency of social media use",
       colour = "Sex")

```

---
# Another Line Graph's Journey

First, inspect the data frame

```{r ash_plot3_view}
head(plot_ash2, 1)
```

--

Luckily, it appears that I do not need to tidy the data beyond what has already been done. So, all I need to do is plot the data

---

#Code for Plotting Another Line Graph

```{r ash_plot3_code, eval=FALSE}
ggplot(plot_ash3, aes(x = age, y = sns_freq_use)) +
  geom_smooth(aes(group = sex, colour = sex), #<<
              method = "lm", se = FALSE, lwd = 2) +
  scale_color_manual(values = c("turquoise3", "purple3")) +
  facet_wrap(~sns, nrow = 1) +
  theme_bw(base_size = 21) +
  labs(title = "Figure 3.",
       subtitle = "Relation between age and frequency of social 
       media use as a function of sex and social media site",
       x = "Age", 
       y = "Frequency of social media use",
       colour = "Sex")
```

---

#Stefania, add whatever plots/code you want! Could you add your pretty table? :)

- Note that I will likely delete one of my figure.. I'm leaning towards Figure 1. Thoughts?

- In case you didn't see this above, you can also insert links like this [click here to view demo for how to modify these slides](https://ashlynnmiller.github.io/Lab14_DemoSlides/).
