---
title: "Outline for the Final Project"
author: "Cameron Kay, Stefania Ashby, and Ashley L. Miller"
date: "October 22nd, 2018"
output:
  html_document:
    highlight: zenburn
    theme: lumen
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 7.5,
                      fig.height = 4.0)

#install required packages
library(rio)
library(here)
library(tidyverse)

#import data
data <- import(here("data", "dataSPSS.sav")) %>%
  janitor::clean_names() %>%
  characterize()

```

### 1) Description of the dataset to be used

We will be using [Pew Research Center's](http://www.pewresearch.org) 
*Core Trends Survey* from January 3-10, 2018. It contains data on `r nrow(data)`
people and nearly `r ncol(data)` variables. The variables primarily concern social
media use, but the dataset also includes participant demographics. 

### 2) Description of preparatory work that will need to be completed

  + **Tidying and Wrangling Data**
      + Considering we will need to create a series of interesting graphics, the bulk of work will consist of tidying the data.  
      + For example, let's say we want to examine whether age trends in social media use differ as a function of social media site (e.g., do older users spend more time on Facebook, whereas younger users spend more time on Snapchat and Instagram?). However, as seen below, the current structure of the data will not allow for this analysis. We will need to convert the data into long format.
 
```{r reload data, include=FALSE}

#For some reason we get a lot of NAs when trying to import the spss file, so I will use the csv file here

data <- import(here("data", "dataCSV.csv")) %>%
  janitor::clean_names()

```

```{r example}

plot_data <- data %>%
  select(age, sns2a, sns2b, sns2c, sns2d, sns2e)

#sns2a = Twitter use
#sns2b = Instagram use
#sns2c = Facebook use
#sns2d = Snapchat use
#sns2e = Youtube use

head(plot_data)

```

  + **Hereherehere**
      + Hereherehere

```{r example2}

print("Here is another example")

```


### 3) Description of how the requirements for the final project will be met.

  + **Hereherehere**
  + **Hereherehere**





