---
title: "Outline for the Final Project"
author: "Cameron Kay, Stefania Ashby, and Ashley L. Miller"
date: "October 22nd, 2018"
output:
  html_document:
    highlight: zenburn
    theme: lumen
    toc: yes
    toc_float: yes
    df_print: paged
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 7.5,
                      fig.height = 4.0)

#install required packages
library(rio)
library(here)
library(tidyverse)

# import data, not applying characterize because it results in NAs where they shouldn't be 
# to use characterize at a later date, we will need to go into the spss file first and make sure all variables that need to be coded have labels.
data <- import(here("data", "dataSPSS.sav")) %>%
  janitor::clean_names()


```

### 1) Description of the dataset to be used

We will be using [Pew Research Center's](http://www.pewresearch.org) 
*Core Trends Survey* from January 3-10, 2018. It contains data on `r nrow(data)`
people and nearly `r ncol(data)` variables. The variables primarily concern social
media use, but the dataset also includes participant demographics. 

```{r look at data}

head(data)

```

### 2) Description of preparatory work that will need to be completed

  + **Tidying and Wrangling Data**
      + As already completed, we will use janitor to clean the names of the columns on import, in addition to converving (via characterize) the SPSS labels. Currently, we cannot use characterize because it results in NAs where there shouldn't be any. In order to use characterize, we will need to first make sure all labels are accurately listed in SPSS before importing to `R`. 
      + We will also need to convert the dataframe to long format using `gather()` and `spread()` from `tidyverse`
          + For example, let's say we want to examine whether age trends in social media use differ as a function of social media site (e.g., do older users spend more time on Facebook, whereas younger users spend more time on Snapchat and Instagram?). However, as seen below, the current structure of the data will not allow for this analysis.  
```{r example}
plot_data <- data %>%
  select(age, sns2a, sns2b, sns2c, sns2d, sns2e)

#sns2a = Twitter use
#sns2b = Instagram use
#sns2c = Facebook use
#sns2d = Snapchat use
#sns2e = Youtube use

head(plot_data)

```

Or, perhaps we want to examine whether age trends in reading differs as a function of book format (e.g. do older readers spend more time with paper copy books whereas younger yousers may spend more time with audiobooks or digital print?). Once again, we will need to transform our data to do this analysis: 
      
```{r example2}

plot_data2 <- data %>% 
  select(age, books1, books2a, books2b, books2c)

# books1 = how many books read in a year?
# books2a	= how many printed books
# books2b	= how many audiobooks
# books2c = how many e-books

head(plot_data2)

```


### 3) Description of how the requirements for the final project will be met.

  + **Requirement (a)**
      + We will generate an APA manuscript produced via the `{papaja}` package in R Markdown, which will include the following sections: an abstract, intro, methods, results, discussion, and references
      + The Introduction will be at least two paragraphs and include two references relevant to our final analyses
  + **Requirement (b)**
      + The project is already hosted on Github, but we will ensure that the final manuscript is fully reproducable
      + Our final R markdown document will demonstrate use of inline code, as well as tidying of the data
          + We will use inline code to provide the mean and standard deviation, as well as the percentages, for our demographic data (i.e., age, gender identity, and cultural identity)
          + We will also use inline code to represent our model in the manuscript (e.g., `time_spent_on_social_media_sites ~ age + social_media_site + (1 | subject)`)
          + Second model idea: `books_read ~ age + book_type + (1 | subject)`
  + **Requirement (c)**
      + We will create at least two graphs
          + Tentative graph 1: geom_point with geom_smooth with method "lm"
              + x-axis: age
              + y-axs: time spent on social media sites
              + colour: social media site
          + Tentative graph 2: geom_bar, facet_wrapped by social media site
              + x-axis: perception of internet as good or bad
              + y-axis: time spent on social media sites
              + facet_wrap: social media site
          + Tentative graph 3: geom_point with geom_smooth with method "lm"
              + x-axis: age
              + y-axis: number books read
              + colour: book format (print, audio, electronic)
  + **Requirement (d)**
      + We will create one table depicting relevant summary statistics, such as... 
          + The mean and sd of the frequency of visiting each social media site overall, as well as bifurcated by gender. 
          + The mean and se of the number of books read for each of the three formats, bifurcated by gender & political party affiliation.
          + A table showing the log-likelihood results of the linear mixed-effects model comparison. 
      + Depending on what we uncover (and on how motivated we feel), we may include a summary of a fitted model described above





