---
title: "Outline for the Final Project"
author: "Cameron Kay, Stefania Ashby, and Ashley L. Miller"
date: "October 22nd, 2018"
output:
  html_document:
    highlight: zenburn
    theme: lumen
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 7.5,
                      fig.height = 4.0)

#install required packages
library(rio)
library(here)
library(tidyverse)

#import data
data <- import(here("data", "dataSPSS.sav")) %>%
  janitor::clean_names() %>%
  characterize()

```

### 1) Description of the dataset to be used

We will be using [Pew Research Center's](http://www.pewresearch.org) 
*Core Trends Survey* from January 3-10, 2018. It contains data on `r nrow(data)`
people and nearly `r ncol(data)` variables. The variables primarily concern social
media use, but the dataset also includes participant demographics. 

### 2) Description of preparatory work that will need to be completed

  + **Tidying and Wrangling Data**
      + As already completed, we will user janitor to the clean the names of the columns on import, in addition to converving (via characterize) the SPSS labels
      + We will also need to convert the dataframe to long format
        + For example, let's say we want to examine whether age trends in social media use differ as a function of social media site (e.g., do older users spend more time on Facebook, whereas younger users spend more time on Snapchat and Instagram?). However, as seen below, the current structure of the data will not allow for this analysis.
        
```{r reload data, include=FALSE}

#For some reason we get a lot of NAs when trying to import the spss file, so I will use the csv file here

data <- import(here("data", "dataCSV.csv")) %>%
  janitor::clean_names()

```

```{r example}

plot_data <- data %>%
  select(age, sns2a, sns2b, sns2c, sns2d, sns2e)

#sns2a = Twitter use
#sns2b = Instagram use
#sns2c = Facebook use
#sns2d = Snapchat use
#sns2e = Youtube use

head(plot_data)

```

```{r example2}

print("Here is another example")

```


### 3) Description of how the requirements for the final project will be met.

  + **Requirement (a)**
      + We will generate an APA manuscript produced via the `{papaja}` package in R Markdown, which will include the following sections: an abstract, intro, methods, results, discussion, and references
      + The Introduction will be at least two paragraphs and include two references relevant to our final analyses
  + **Requirement (b)**
      + The project is already hosted on Github, but we will ensure that the final manuscript is fully reproducable
      + Our final R markdown document will demonstrate use of inline code, as well as tidying of the data
        + We will use inline code to provide the mean and standard deviation, as well as the percentages, for our demographic data (i.e., age, gender identity, and cultural identity)
        + We will also use inline code to represent our model in the manuscript (e.g., `time_spent_on_social_media_sites ~ age + social_media_site + (1 | subject)`)
  + **Requirement (c)**
      + We will create at least two graphs
        + Tentative graph 1: geom_point with geom_smooth with method "lm"
          + x-axis: age
          + y-axs: time spent on social media sites
          + colour: social media site
        + Tentative graph 2: geom_bar, facet_wrapped by social media site
          + x-axis: perception of internet as good or bad
          + y-axis: time spent on social media sites
          + facet_wrap: social media site
  + **Requirement (d)**
      + We will create one table depicting relevant summary statistics, such as... 
        + The mean and sd of the frequency of visiting each social media site overall, as well as bifurcated by gender. 
        + A table showing the log-likelihood results of the linear mixed-effects model comparison. 
      + Depending on what we uncover (and on how motivated we feel), we may include a summary of a fitted model described above





